### 2022-07-12 supplemental/supplemental.tex

\IEEEPARstart{T}his document contains a description of additional experiments to find a performant
stimulus generation method and a discussion of sparsity in tinnitus signals.
The code for all experiments is freely available at \url{https://github.com/alec-hoyland/tinnitus-project}
and the data are available upon request.

@@

\subsection{Auditorally-Distinguishable Stimuli}

We used mel-frequency binning to ensure that our stimuli were auditorally-distinguishable.
The mel scale is a perceptual scale of pitches judged by listeners to be equal in distance
from one to another (Fig. \ref{fig:hz2mel}) \cite{hamiltonTopographySpeechrelatedAcoustic2020}.

@@

Furthermore, to reduce the system complexity by more than 80x,
we implement tonotopic binning, where the frequency scale is binned
along $100$ equally mel-spaced bins (Fig. \ref{fig:examplestimulus}).

@@

@@

>>>>

\IEEEPARstart{T}HIS document contains a description of additional experiments to find a performant
stimulus generation method and a discussion of sparsity in tinnitus signals.
The code for all experiments is freely available at \url{https://github.com/alec-hoyland/tinnitus-project}
and the data are available upon request.

@@

We used mel-frequency binning to ensure that our stimuli were auditorally-distinguishable.
The mel scale is a perceptual scale of pitches judged by listeners to be equal in distance
from one to another (Fig. \ref{fig:hz2mel}) \cite{hamiltonTopographySpeechrelatedAcoustic2020}.
Figure \ref{fig:examplestimulus} shows an example generated stimulus.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{gfx/binned_vs_unbinned_spect.eps}
	\caption{Binned spectra capture the salient characteristics of unbinned spectra.
  \textbf{(a)} shows the spectrum for the ``buzzing'' ATA tinnitus example
  (black) and its binned version (red). \textbf{(b)} shows the same for the ``buzzing'' example.}
	\label{fig:binned_vs_unbinned_spect}
\end{figure}

Furthermore, to reduce the system complexity by more than 80x,
we implement tonotopic binning, where the frequency scale is binned
along $100$ equally mel-spaced bins (Fig. \ref{fig:binned_vs_unbinned_spect}).
This has the effect of smoothing some peaks of the spectra
as well as reducing the dimensionally by a factor of 80x.
Despite the dimensionality reduction, less than 10\% of information is lost.

@@

\subsection{Hyperparameter Sweep Results}

@@

\subsection{Human vs. Synthetic Performance}

For the hyperparameter sweep, we relied heavily on a synthetic model subject
who made the yes/no decisions.
This model relies on an idealized process,
in which the \textit{in-silico} subject compares
the incoming stimuli to an internal representation in a purely linear process.
The \textit{in-silico} subject is internally consistent over trials,
something which subjects have self-reported as not necessarily being true.
In the \textsc{Conclusion} of the paper, we discuss some of the reasons,
namely, that the yes/no decision threshold may not be fixed for a human subject,
but instead varies as the subject drifts and overcorrects during the trial.
Figure \ref{fig:r2_vs_trials} shows
reconstruction accuracy measured by Pearson $r^2$ as a function of the
number of trials.
Synthetic performance increases monotonically as a function of the number of trials,
but human performance drops consistently after 1,600 trials.
We hypothesis that decision drift and subject fatigue are the main causes.

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{gfx/r2_vs_trials.eps}
	\caption{Performance for human subjects on the task is non-monotonic,
  contrasting with theoretical and synthetic results.
  \textbf{(a)} shows synthetic and human subject reconstruction accuracy
  as measured by Pearson's $r^2$ as a function of number of trials
  for the ``buzzing'' condition. \textbf{(b)} shows results for the ``roaring'' condition.}
	\label{fig:r2_vs_trials}
\end{figure}
